### 2018-08-08 paper/approach.tex
up

Finally, we introduce the complete \ac{SPORES} protocol, which 
allows the device \squad to act as an autonomous system (Figure~\ref{fig:outline} \ding{204}).
In particular, we introduce a protocol which allows transferring larger 
messages by fragmentation and reassembly across the devices in the \squad.

>>>>

Finally, we introduce the complete \ac{SPORES} protocol that acts as a private P2P file transfer. It 
allows the device \squad to act as an autonomous system.
In particular, we introduce a protocol which allows transferring larger 
messages by fragmentation and reassembly across the devices in the \squad  (Figure~\ref{fig:outline} \ding{204}).
